\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 design.tex
patch up design

\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\textwidth]{landslide.png}
	\caption{A simple visualisation of Landslide and its components, and how they interact with the guest kernel.}
	\label{fig:landslide}
\end{figure}

@@

The Landslide scheduler also tracks which important actions each thread is performing. These actions are {\em forking}, {\em vanishing}, and {\em sleeping}, which are described in the next section \revision{(note that ``vanish'' is simply Pebbles's name for ``exit'')}, and also {\em in\_timer\_handler} and {\em in\_context\_switch}, which express what type of context switch a given thread may be performing, and are useful for both thread scheduling (Section~\ref{sec:components-inflight}) and detecting voluntary reschedules (Section~\ref{sec:components-arbiter}).\footnote{
There are also other minor actions: {\em readlining}, used to track test lifecycle (Section~\ref{sec:components-test}), {\em just\_forked}, used for special-case context switch behaviour (Section~\ref{sec:components-arbiter}), and also several flags for tracking mutex lock/unlock events.}

@@

The Landslide scheduler relies on the guest kernel informing it about certain important events in the thread lifecycle. The guest kernel does this by means of annotations (which are described in Section~\ref{sec:using-annotations}). Algorithm~\ref{alg:tell-landslide} shows how Landslide handles these annotations internally.\footnote{
There are also cases for the runqueue annotations, \texttt{tell\_landslide\_on\_rq} and \texttt{tell\_landslide\_off\_rq}, which we omit for brevity. One important note is that the routine for \texttt{tell\_landslide\_on\_rq} must also check the ``forking'' flag, in case the kernel's \texttt{fork} implementation does not immediately switch to the new thread but instead adds it to the runqueue for later.}

@@

Landslide's scheduling technique, called the {\em schedule in-flight}, involves successive triggering of timer interrupts to trigger context switches until the desired thread begins to run. Algorithm~\ref{alg:inflight} shows how Landslide makes this happen.

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=0.65\textwidth]{landslide.png}
	\caption{A simple visualisation of Landslide and its components, and how they interact with the guest kernel.}
	\label{fig:landslide}
\end{figure}

@@

The Landslide scheduler also tracks which important actions each thread is performing. These actions are {\em forking}, {\em vanishing}, and {\em sleeping}, which are described in the next section \revision{(note that ``vanish'' is simply Pebbles's name for ``exit'')}, and also {\em in\_timer\_handler} and {\em in\_context\_switch}, which express what type of context switch a given thread may be performing (voluntary reschedule, etc), and are useful for both thread scheduling (Section~\ref{sec:components-inflight}) and detecting voluntary reschedules (Section~\ref{sec:components-arbiter}).\footnote{
There are also other minor actions: {\em readlining}, used to track test lifecycle (Section~\ref{sec:components-test}), {\em just\_forked}, used for special-case context switch behaviour (Section~\ref{sec:components-arbiter}), and also several flags for tracking mutex lock/unlock events.}

@@

The Landslide scheduler relies on the guest kernel to inform it about certain important events in the thread lifecycle. The guest kernel does this by means of annotations (which are described in Section~\ref{sec:using-annotations}). Algorithm~\ref{alg:tell-landslide} shows how Landslide handles these annotations internally.\footnote{
There are also cases for the runqueue annotations, \texttt{tell\_landslide\_on\_rq} and \texttt{tell\_landslide\_off\_rq}, which we omit for brevity. One important note is that the routine for \texttt{tell\_landslide\_on\_rq} must also check the ``forking'' flag, in case the kernel's \texttt{fork} implementation does not immediately switch to the new thread but instead adds it to the runqueue for later.}

@@

Landslide's scheduling technique, called the {\em schedule in-flight}, involves successively injecting timer interrupts to trigger context switches until the desired thread begins to run. Algorithm~\ref{alg:inflight} shows how Landslide makes this happen.
